A\HT{n Elastica-driven} Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-07-07 jmiv.tex
avances

However length regularization shows limitations when segmenting
small or thin and elongated objects, as it tends to shrink solutions
or \HT{yields} disconnected solutions. Such drawbacks can be problematic in
image segmentation or image inpainting. It is thus rather natural to
consider curvature (especially squared curvature) \HT{as} a potential
regularizer. Energies involving \HT{both length and} squared curvature are often called
{\em Euler elastica} model (\HT{that} dates back to Euler) or {\em Willmore energy}
($n$-dimensional extension) and have been brought back to attention in
computer vision by Mumford \cite{mumford1994elastica}. A similar
regularizer is also present in the second-order regularizer
of the \HT{original} snake model \cite{kass1988snakes}. \HT{Similarly,
an explicit curvature term was often employed in early level-set methods,
like~\cite{malladi1995image,malladi1995shape,ballester01filljoint} for segmentation or inpainting,}
\HT{However, Casselles {\em et al.} in~\cite{casseles97geodesic} observed that these
terms were not geometric, in the sense that they depended on the discretization}.

The use of curvature for surface regularization was studied in~\cite{bobenko2005discrete},
although results look promising, authors used an inexact linearized version of the
square curvature at every step.

One of the first successful uses of \HT{geometric squared} curvature in image processing is the inpainting algorithm
described in \cite{masnou98inpainting}\HT{, where authors} evaluate the elastica energy along the level lines of a
simply-connected image to reconstruct its occluded parts. The non-intersection property of level lines \HT{induces} the
construction of an efficient dynamic programming algorithm. \HT{However, } the curvature energy is \HT{only} coarsely
approximated.  \cite{chan02elasticainpainting} \HT{is} another geometric inpainting method involving elastica
\HT{optimized with level-sets}.

In image segmentation, Zehiry and Grady have shown that injecting curvature as a regularizer \HT{can help} recover thin
and elongated objects \cite{zehiry10fast}. Similarly Schoenemann {\em et al.}  \cite{schoenemann09linear} have
considered the elastica energy in their ratio-based image segmentation approach. In~\cite{schoenemann2011elastic},
Schoenemann~{\em et al.} extend ratio-cut approaches to segmentation with a curvature term. Their global optimization
framework shows the considerable \HT{advantages} of using such regularizer in common binary image segmentation tasks.
However the time complexity of their algorithm \HT{is prohibitive,} even if curvature is \HT{again} coarsely
approximated.  In more recent work, Lim {\em et al.} propose an edge-weighted Willmore-like flow to segment
vertebra~\cite{lim2012introducing} using a level-set formulation.  They observe improved results compared
to~\cite{casseles97geodesic} and other perimeter-based priors, but observe that a shape prior and a close-enough
solution must also be provided to achieve good results.

In fact, it is still a very challenging task to inject curvature in
the context of image segmentation.  
\HT{State-of-art methods are in practice} difficult to optimize and \HT{do not scale}
\cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In
order to achieve reasonable running times, such approaches make use of
coarse curvature estimations for which the approximation error is
\HT{often} unknown. Improving the quality of the curvature estimator has an
important impact on the accuracy of the results, but is
computationally too costly in these methods.

Segmentation methods using Elastica or Willmore energies \HT{generally
reduce to} computing the corresponding flow, i.e. following its
gradient. Well-founded level-set methods involving Willmore energy
\cite{droske2004level} have been used in medical image segmentation
\cite{lim2012introducing}. Another level-set formulation similar to
the Chan-Vese model \HT{was} proposed in \cite{zhu2013image}. Willmore
flow can also be carried out by phase-field models (see
\cite{bretin2015phase}) but they are less suited to image segmentation
since interfaces are blurred in such models. Threshold dynamics can
also be considered for such energies \cite{esedoglu2008threshold} and
has been proposed for image desocclusion \cite{esedoglu2005threshold}.

@@

\begin{itemize}
\item{Geometric properties and regularization}
\item{The role of curvature}

@@

\item{What are the difficulties in use curvatue as a regularizer (point out convex relaxation approaches) and how a digital approach may help us }
\item{Outline: We present two models that illustrate how digital estimators can be used to minimize the elastica energy on digital sets.  }
\item{\todo{Add related works : geometric priors, binary segmentation, other digital curve evolution models}}
\item{\todo{Talk about Willmore flow with phase field or with threshold dynamics}}

@@

\item{\textbf{Convex relaxation}}
  \begin{itemize}
  \item{A convex lower semicontinuous approximation of Eulers elastica energy \cite{bredies15convex}}
  \item{Introducing Total Curvature for Image Processing \cite{goldluecke11totalcurvature}}
  \end{itemize}

\item{\textbf{Constraint optimization}}
  \begin{itemize}
  \item{Curvature regularity for region-based image segmentation and inpainting: A linear programming relaxation \cite{schoenemann09linear} }	
  \item{A Fast Algorithm for Euler's Elastica Model Using Augmented Lagrangian Method \cite{tai11elastica} }		
  %%\item{The elastic ratio: Introducing curvature into ratio-based image segmentation \cite{schoenemann2011elastic}
  %%}		%% DONE
  \item{Curvature Regularization for Curves and Surfaces in a Global Optimization Framework \cite{strandmark11globalframework} }
  \end{itemize}

>>>>

However length regularization shows limitations when segmenting small or thin and elongated objects, as it tends to
shrink solutions or \HT{yields} disconnected solutions. Such drawbacks can be problematic in image segmentation, image
restoration or image inpainting. It is thus rather natural to consider curvature (especially squared curvature) \HT{as}
a potential regularizer. Energies involving \HT{both length and} squared curvature are often called \HT{the {\em Elastica}}
model (\HT{that} dates back to Euler) . \HT{The {\em Willmore energy} is its $n$-dimensional extension. These were brought to
attention} in computer vision by Mumford \cite{mumford1994elastica}. A similar concept is also present in the
second-order regularizer of the \HT{original} snake model \cite{kass1988snakes}. \HT{Indeed, an explicit curvature
  term was often employed in early level-set methods, like~\cite{malladi1995image,malladi1995shape,ballester01filljoint}
  for segmentation or inpainting,} \HT{However, Casselles {\em et al.} in~\cite{casseles97geodesic} observed that these
  terms as employed were not geometric, in the sense that they depended on the discretization parameters}.

\HT{The use of curvature for surface regularization in the case of the Willmore energy was studied
  in~\cite{bobenko2005discrete}, although results look promising, authors used an inexact linearized version of the
  square curvature at every step.}

One of the first successful uses of \HT{geometric, squared} curvature in image processing is the inpainting algorithm
described in \cite{masnou98inpainting}\HT{, where authors} evaluate the elastica energy along the level lines of a
simply-connected image to reconstruct its occluded parts. The non-intersection property of level lines \HT{induces} the
construction of an efficient dynamic programming algorithm. \HT{However, } the curvature energy is \HT{only} coarsely
approximated.  \cite{chan02elasticainpainting} \HT{is} another geometric inpainting method involving elastica
\HT{optimized with level-sets}.

In image segmentation, Zehiry and Grady have shown that injecting curvature as a regularizer \HT{can help} recover thin
and elongated objects \cite{zehiry10fast}. Similarly Schoenemann {\em et al.}  \cite{schoenemann09linear} have
considered the elastica energy in their ratio-based image segmentation approach. In~\cite{schoenemann2011elastic},
Schoenemann~{\em et al.} extend ratio-cut approaches to segmentation with a curvature term. Their global optimization
framework shows the considerable \HT{advantages} of using such regularizer in common binary image segmentation tasks.
However the time complexity of their algorithm \HT{is prohibitive,} even if curvature is \HT{again} coarsely
approximated.  \HT{In more recent work, Lim {\em et al.} propose an edge-weighted Willmore-like flow to segment
vertebra~\cite{lim2012introducing} using a level-set formulation. They observe improved results compared
to~\cite{casseles97geodesic} and other perimeter-based priors, but observe that a shape prior and a close-enough
solution must also be provided to achieve good results.}

In fact, it is still a very challenging task to \HT{efficiently handle} curvature in the context of image segmentation.
\HT{State-of-art methods are in practice} difficult to optimize and \HT{do not scale easily}
\cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In order to achieve
reasonable running times, such approaches make use of coarse curvature estimations for which the approximation error is
\HT{often} unknown. Improving the quality of the curvature estimator has an important impact on the accuracy of the
results, but is computationally too costly in these methods.

Segmentation methods using Elastica or Willmore energies \HT{can be formulated via the computation of} corresponding
flow, i.e. following its gradient. Well-founded level-set methods involving Willmore energy \cite{droske2004level} have
been used in medical image segmentation \cite{lim2012introducing}. Another level-set formulation similar to the
Chan-Vese model \HT{was} proposed in \cite{zhu2013image}. Willmore flow can also be carried out by phase-field models
(see \cite{bretin2015phase}) but they are less suited to image segmentation since interfaces are blurred in such
models. Threshold dynamics can also be considered for such energies \cite{esedoglu2008threshold} and has been proposed
for image desocclusion \cite{esedoglu2005threshold}. \HT{However, flow-based methods will always deliver
  a local minimum, which heavily depend on initialization for good results}.

\HT{In contrast, researchers have sought convex relaxation of curvature-related
  formulation. In~\cite{goldluecke11totalcurvature}, Goldluecke and Cremers introduce the {\em Total Curvature}, based
  on the Menger-Melnikov curvature of a measure. The formulation is non-convex but can be relaxed into a well-correlated
  but non-tight convex one. The relaxed formulation can be used to solve inverse problems including segmentation,
  however computing a solution is still expensive, requiring signifiant parallelisation efforts with a GPU to achieve
  acceptable computing times}. \HT{In~\cite{bredies15convex}, Bredies {\em et al.} study a convex approximation of the
  Elastica energy, using a lifting scheme. Thanks to the lifting, it is not restritcted to binary sets. It shows
  promising results and can be used for image restoration in addition to inpainting and segmentation. The scheme is
  however neither tight nor exact, and required 4 dimensions for a 2D approximation. In addition, it does not carry over
  to $nD$. It also remains computationally expensive.}

@@

\begin{itemize}
%% \item{Geometric properties and regularization}
%% \item{The role of curvature}

@@

\item{What are the difficulties in use curvature as a regularizer (point out convex relaxation approaches) and how a digital approach may help us }
\item{Outline: We present two models that illustrate how digital estimators can be used to minimize the elastica energy on digital sets.  }
\item{\todo{Add related works : geometric priors, binary segmentation, other digital curve evolution models}}
\item{\todo{Talk about Willmore flow with phase field or with threshold dynamics}}

@@

%%\item{\textbf{Convex relaxation}}
%%  \begin{itemize}
%%  \item{A convex lower semicontinuous approximation of Eulers elastica energy \cite{bredies15convex}}
 %% \item{Introducing Total Curvature for Image Processing \cite{goldluecke11totalcurvature}}
 %% \end{itemize}

\item{\textbf{Constraint optimization}}
  \begin{itemize}
 %% \item{Curvature regularity for region-based image segmentation and inpainting: A linear programming relaxation \cite{schoenemann09linear} }	
  \item{A Fast Algorithm for Euler's Elastica Model Using Augmented Lagrangian Method \cite{tai11elastica} }		
  %%\item{The elastic ratio: Introducing curvature into ratio-based image segmentation \cite{schoenemann2011elastic}
  %%}		%% DONE
  \item{Curvature Regularization for Curves and Surfaces in a Global Optimization Framework \cite{strandmark11globalframework} }
  \end{itemize}
